Learning constraints in spreadsheets and tabular data

### 2016-06-07 Paper/ECAI/tabular.tex
removing and moving the figures from and back

\begin{figure}[t]
  \centering
  \includegraphics[width=1\linewidth]{figures/tabletool.png}
  \caption{This simple table selection tool allows users to select rectangular ranges of cells corresponding to (headerless) tables.
  An explicit orientation can also be provided.}
  \label{fig:visual_tool}
\end{figure}

@@

\paragraph{Visual}
The above assumptions do not hold for many tables. However, since the specification of tables is usually easy for humans, we propose a second approach which allows users to indicate tables using a visual tool (Figure~\ref{fig:visual_tool}).
Users select tables excluding the header and optionally specify an orientation.
The tool then generates the specification of the tables automatically.

@@

\subsection{Error detection}
\begin{figure*}[thb]
\begin{subfigure}{.70\textwidth}
  \begin{center}
    \includegraphics[width=\textwidth]{figures/fbi_figure_highlighted.png}
  \end{center}
  \caption{Real world tabular constraint reconstruction: FBI crime statistics}
  \label{fig:fbi}
\end{subfigure}
\hfill
\begin{subfigure}{.29\textwidth}
\begin{center}
    \includegraphics[width=\textwidth]{figures/autocompletion_example.png}
  \end{center}
  \caption{\sergey{Samuel, Tias have a look at it, should be corrected and extended, like with groups indications and formulas?}}
  \label{fig:autocompletion_example}
\end{subfigure}
\end{figure*}

@@

The second type of error detection is \textit{offline} and attempts to detect errors in a spreadsheet.
Consider a use case concerning crime statistics provided by the FBI in Figure~\ref{fig:fbi}.
Our system is able to detect the second sum constraint, however, a missing value prevents the first sum constraint from being learned.
A possible approach to detect such missing or wrong values is to look at a sample of the table, e.g. trying to leave out each row, and compare the constraints learned on this sample with the constraints learned on the whole table.
%The sample needs to be large enough such that we have enough confidence that the constraints are correct. For example, in Figure \ref{fig:fbi} all but one row satisfy the constraint, which is a strong indication that there is a constraint violation.
If we define the sample to be the snapshot data and the other row(s) to be the additional input~$\Delta D$, this task can be formulated as online error detection and dealt with in the same way.
%Of course, generating large enough samples and rows (columns) to be added can be done in multiple ways.
%In the limited case of detecting single errors one can leave out every row (column), consider the remaining data to be the sample and
%and the left out row (column) to be new input.

>>>>

% \begin{figure}[t]
%   \centering
%   \includegraphics[width=1\linewidth]{figures/tabletool.png}
%   \caption{This simple table selection tool allows users to select rectangular ranges of cells corresponding to (headerless) tables.
%   An explicit orientation can also be provided.}
%   \label{fig:visual_tool}
% \end{figure}

@@

\paragraph{Visual}
The above assumptions do not hold for many tables. However, since the specification of tables is usually easy for humans, we propose a second approach which allows users to indicate tables using a visual tool.% (Figure~\ref{fig:visual_tool})
Users select tables excluding the header and optionally specify an orientation.
The tool then generates the specification of the tables automatically.

@@

\subsection{Error detection}
\begin{figure}[thb]
% %\begin{subfigure}{.70\textwidth}
%   \begin{center}
%     \includegraphics[width=\width]{figures/fbi_figure_highlighted.png}
%   \end{center}
%   \caption{Real world tabular constraint reconstruction: FBI crime statistics}
%   \label{fig:fbi}
%\end{subfigure}
% \hfill
% \begin{subfigure}{.29\textwidth}
\begin{center}
    \includegraphics[width=0.60\linewidth]{figures/autocompletion_example.png}
  \end{center}
  \caption{\sergey{Samuel, Tias have a look at it, should be corrected and extended, like with groups indications and formulas?}}
  \label{fig:autocompletion_example}
%\end{subfigure}
\end{figure}

@@

The second type of error detection is \textit{offline} and attempts to detect errors in a spreadsheet.
% Consider a use case concerning crime statistics provided by the FBI in Figure~\ref{fig:fbi}.
% Our system is able to detect the second sum constraint, however, a missing value prevents the first sum constraint from being learned.
% A possible approach to detect such missing or wrong values is to look at a sample of the table, e.g. trying to leave out each row, and compare the constraints learned on this sample with the constraints learned on the whole table.
  %The sample needs to be large enough such that we have enough confidence that the constraints are correct. For example, in Figure \ref{fig:fbi} all but one row satisfy the constraint, which is a strong indication that there is a constraint violation.
If we define the sample to be the snapshot data and the other row(s) to be the additional input~$\Delta D$, this task can be formulated as online error detection and dealt with in the same way.
%Of course, generating large enough samples and rows (columns) to be added can be done in multiple ways.
%In the limited case of detecting single errors one can leave out every row (column), consider the remaining data to be the sample and
%and the left out row (column) to be new input.
